---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
First of all, load required package from here.
```{r}
library(stats)
library(base)
library(dplyr)
library(ggplot2)
```

For Analysis, load data and assign in to object 'activity.
```{r}
activity <- read.csv('activity.csv')
```

Here are several samples of data.
```{r}
head(activity)
```

There are 3 variables : 'steps', 'date', 'interval', which of 3 means  
- steps : Number of steps taking in a 5-minute interval  
- date : The date on which the measurement was taken  
- interval : Identifier for the 5-minute interval in which measurement was taken


## What is mean total number of steps taken per day?
First, group the original data by date. And calculate 
total numbers of steps of each date group.

```{r}
total_step_per_day <- activity %>% group_by(date) %>% 
  summarize(total=sum(steps, na.rm = TRUE))
```

Here are several results of this calculation.
```{r}
head(total_step_per_day)
```

And plot histogram of it.
```{r}
hist(total_step_per_day$total, 
     xlab = 'Steps', ylab = 'Frequency(days)',
     main = 'Total number of steps per day')
```

And then, calculate the mean and median of these total number of steps
```{r}
mean_steps_per_day <- mean(total_step_per_day$total)
median_steps_per_day <- median(total_step_per_day$total)
mean_steps_per_day
median_steps_per_day
```

the mean value is '~~~', and the median value is '~~~'.


## What is the average daily activity pattern?
To examine it, We will make Make a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis).  
For this, We will group the original data by interval value, and
calculate the average value of steps of each interval group.  
The following is the code to do that.

```{r}
aver_steps_per_5min <- activity %>% group_by(interval) %>%
  summarize(aver = mean(steps, na.rm = TRUE))
```

and plot it.
```{r}
with(aver_steps_per_5min, 
     plot(interval, aver, type = 'l', xlab='Interval',
          ylab='Steps', main='Average number of steps per 5-minutes'))
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
interval_max <- 
  aver_steps_per_5min$interval[which.max(aver_steps_per_5min$aver)]
interval_max
```

The interval that contain maximum number of steps is, '~~~~'.


## Imputing missing values
And let's impute missing values.  
How many missing values in the original dataset(object 'activity')?
```{r}
total_NA <- sum(is.na(activity$steps))
total_NA
```
There are '~~~~' of missing values.  
Let's fill it with the average number of steps per each of 5-minutes interval.

```{r}
NA_data <- activity[is.na(activity$steps),]

for(i in 1:2304){
  NA_data$steps[i] <- aver_steps_per_5min$aver[aver_steps_per_5min$interval 
                                               == NA_data$interval[i]]
}
```

Here are some samples of the result value that we filled.
```{r}
head(NA_data)
```

And then let's make a new dataset by putting filled data into the original dataset!
```{r}
New_activity <- activity
New_activity[is.na(activity$steps),] <- NA_data
```

If we check there are missing values in new dataset,
```{r}
sum(is.na(New_activity))
```

There is no missing value.  
Let's See the total number of steps taken each day again with our new dataset!
```{r}
New_total_steps_per_day <- New_activity %>% group_by(date) %>%
  summarize(total=sum(steps))
hist(New_total_steps_per_day$total, 
     xlab = 'Steps', ylab = 'Frequency(days)',
     main = 'Total number of steps per day')
```

And also calculate the mean and median value again.
```{r}
New_mean_per_day <- mean(New_total_steps_per_day$total)
New_median_per_day <- median(New_total_steps_per_day$total)
New_mean_per_day
New_median_per_day
```

the mean value of total number of steps per each day is '~~~'  
the median value of it is '~~~', in comparison with the fact that each of those values are '~~~', '~~~' in original data.



## Are there differences in activity patterns between weekdays and weekends?
To figure out it, we will make new variable 'level' that indicates whether a given date is a weekday or weekend day.  
To do it, we convert the 'date' variable from 'character' class into 'Date' class.
```{r}
weekday <- c('월요일', '화요일', '수요일', '목요일', '금요일')
weekend <- c('토요일', '일요일')
New_activity$date <- as.Date(New_activity$date, format = "%Y-%m-%d")
```

And then assign the 'level' value('weekday' or 'weekend') to each rows of data in according to the result value of 'weekdays()' function of 'date' variable.
```{r}
for(i in 1:nrow(New_activity)){
  if(weekdays(New_activity$date[i]) %in% weekday){
    New_activity$level[i] <- 'weekday'
  } else if(weekdays(New_activity$date[i]) %in% weekend){
    New_activity$level[i] <- 'weekend'
  }
}
```

And let's see the time-series average number of steps take for 5-minutes interval for each level.  
For this, group the new data with added 'level' column by level and calculate the mean value for each groups

```{r}
two_level_activity <- New_activity %>% group_by(level, interval) %>% 
  summarize(average=mean(steps))
```

And plot it.
```{r}
g <- qplot(interval, average, data = two_level_activity, geom = 'line',
      facets=level~., 
      color=level, xlab = 'Interval', ylab = 'Steps',
      main = 'Average number of steps per 5-minutes interval')
g + theme(plot.title=element_text(hjust=0.5))
```







